Revisiting the Truisms of Software Engineering:\\ Does Phase Delay Dramatically Increases Repair Time?

### 2015-03-11 phaseDelay.tex
Phase delay in slower bugs  is now a subsection
Added discussion and conclusion section outlines

\section{Phase Delay in Slower Bugs?}
In these results, we checked if a small number of bugs are most expensive. 
To check this:
\bi
\item
We repeated the analysis that generated \fig{scale},
but instead of looking at the 50th percentile, we displayed the scale up factors
\item 
We only
checked the Design and Code scale up results since, from \fig{scale}, it is clear these
have the most examples of longest phase delays.
\ei 
The  results are shown in \fig{scale90} and these
results are somewhat different for Design and Coding issues: 
\bi 
\item For Design issues,  these have the same
general form as the 50th percentile results. That is, while it it certainly faster
to remove thing sin the phase where they are created, once we leave that phase
it does not seem to matter much how many phases we wait before fixing the issue.
\item
\item For Coding issues, the seems little impact of phase delay on the time
required to fix.
\ei

@@

\begin{figure}
\begin{center}
\scriptsize\begin{tabular}{|l@{~:~}l|}\hline
Bug Prediction Dataset &http://bug.inf.usi.ch \\
Eclipse Bug Data &http://goo.gl/tYKahN \\
FLOSSMetrics& http://flossmetrics.org \\
FLOSSMole &http://flossmole.org \\
IBSBSG& http://www.isbsg.org \\
ohloh& http://www.openhub.net \\
PROMISE &http://promisedata.googlecode.com \\
Qualitas Corpus &http://qualitascorpus.com \\
Software Artifact Repository &http://sir.unl.edu \\
SourceForge Research Data &http://zerlot.cse.nd.edu \\
Sourcerer Project &http://sourcerer.ics.uci.edu \\
Tukutuku &http://www.metriq.biz/tukutuku \\
Ultimate Debian Database &http://udd.debian.org\\\hline
\end{tabular}
\end{center}
\caption{Some repositories of software engineering data.}\label{fig:sedata}
\end{figure}
The data collected in the SEI TSP databases contains 
extensive process details
including a detailed phased breakdown showing what happened at what
phases of the lifecycle. This makes this data somewhat different to the standard
 publicly available
software projects data sets currently available to 
SE researchers. Most of the \fig{sedata} data sets have software product information
such as full source code, or summaries of static features.
A subset of that data contain issue or defect reports and/or
the time taken to build these systems.  We are unaware
of any of these having detailed phase-by-phase breakdowns of project data.

\section*{Acknowledgements}
This work was partially funded by an National Science
Foundation grant NSF-CISE 1302169.

>>>>

\subsection{Phase Delay in Slower Bugs?}
In these results, we checked if a small number of bugs are most expensive. 
To check this:
\bi
\item
We repeated the analysis that generated \fig{scale},
but instead of looking at the 50th percentile, we displayed the scale up factors
\item 
We only
checked the Design and Code scale up results since, from \fig{scale}, it is clear these
have the most examples of longest phase delays.
\ei 
The  results are shown in \fig{scale90} and these
results are somewhat different for Design and Coding issues: 
\bi 
\item For Design issues,  these have the same
general form as the 50th percentile results. That is, while it it certainly faster
to remove thing sin the phase where they are created, once we leave that phase
it does not seem to matter much how many phases we wait before fixing the issue.
\item
\item For Coding issues, the seems little impact of phase delay on the time
required to fix.
\ei

@@

 \section{Discussion}
 \todo{
 \bi
    \item summarize analysis findings
    \item Offer interpretations of findings, e.g., why might these things be so
 \ei
 }

 \section{Conclusion}
 \todo{
 \bi
    \item Summarize data tested - survey + TSP data
    \item reiterate hypothesis testing results
    \item Restate the motivation: widely-held beliefs need to be revisted. 
    \item We now have evidence, from 5 different sources, that phase delay does not seem to hold under certain conditions (although our study is by far the biggest in terms of data points).
    \item phase delay may still apply in some (many?) projects, but clearly it does not in all. This has huge implications for, e.g., cost modeling, effort prediction.
 \ei
 }

% \section{Related Work}

% \begin{figure}
% \begin{center}
% \scriptsize\begin{tabular}{|l@{~:~}l|}\hline
% Bug Prediction Dataset &http://bug.inf.usi.ch \\
% Eclipse Bug Data &http://goo.gl/tYKahN \\
% FLOSSMetrics& http://flossmetrics.org \\
% FLOSSMole &http://flossmole.org \\
% IBSBSG& http://www.isbsg.org \\
% ohloh& http://www.openhub.net \\
% PROMISE &http://promisedata.googlecode.com \\
% Qualitas Corpus &http://qualitascorpus.com \\
% Software Artifact Repository &http://sir.unl.edu \\
% SourceForge Research Data &http://zerlot.cse.nd.edu \\
% Sourcerer Project &http://sourcerer.ics.uci.edu \\
% Tukutuku &http://www.metriq.biz/tukutuku \\
% Ultimate Debian Database &http://udd.debian.org\\\hline
% \end{tabular}
% \end{center}
% \caption{Some repositories of software engineering data.}\label{fig:sedata}
% \end{figure}
% The data collected in the SEI TSP databases contains 
% extensive process details
% including a detailed phased breakdown showing what happened at what
% phases of the lifecycle. This makes this data somewhat different to the standard
%  publicly available
% software projects data sets currently available to 
% SE researchers. Most of the \fig{sedata} data sets have software product information
% such as full source code, or summaries of static features.
% A subset of that data contain issue or defect reports and/or
% the time taken to build these systems.  We are unaware
% of any of these having detailed phase-by-phase breakdowns of project data.

\section*{Acknowledgements}
This work was partially funded by an National Science
Foundation grants NSF-CISE 1302169 and CISE 1302169.
